Lower Bounds on the Minimax Risk for the \\ Source Localization Problem

### 2017-05-08 paper.tex
Fix link for full version.

\begin{figure}[t]
	\centering
	\includegraphics[width=2.8in]{lb-vs-m-annotated}
	\vspace{-3pt}
	\caption{A numerically generated plot of the lower bound on minimax risk of
		source localization, against the number of uniformly distributed
		sensors, $m$, used to estimate the location (code available
		online~\cite{Code}). The different curves are for different numbers of
		``trials'', $n$ (number of i.i.d.\ sensor observations). The bound
		saturates for large $m$, indicating that for a \emph{fixed} number of
		trials, there is decreasing benefit to using more sensors.  However,
		the plot suggests that with more trials, the bound saturates at
		increasingly larger numbers of sensors. Thus, there may be benefit to
		increasing the number of sensors when you have more trials.}
	\label{fig:numerical}
\end{figure}

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[width=2.8in]{lb-vs-m-annotated}
	\vspace{-3pt}
	\caption{A numerically generated plot of the lower bound on minimax risk of
		source localization, against the number of uniformly distributed
		sensors, $m$, used to estimate the location (code available
		online~\cite{FullVersion}). The different curves are for different
		numbers of ``trials'', $n$ (number of i.i.d.\ sensor observations). The
		bound saturates for large $m$, indicating that for a \emph{fixed}
		number of trials, there is decreasing benefit to using more sensors.
		However, the plot suggests that with more trials, the bound saturates
		at increasingly larger numbers of sensors. Thus, there may be benefit
		to increasing the number of sensors when you have more trials.}
	\label{fig:numerical}
\end{figure}
